p-adic stability in linear algebra

### 2015-01-18 examples/stability.tex
\todo{} fixed

\noindent
{\bf Notations.}
Throughout the paper, the letter $K$ will refer to a complete 
discrete valuation field of characteristic $0$, that is either a finite 
extension of the field of $p$-adic numbers $\Qp$ or a field of Laurent 
series over a field of characteristic $0$ \todo{what about mixed characteristic with infinite residue field?}.
We denote by $\val : K \to \Z 
\cup \{+\infty\}$ of $K$ --- it is the $p$-adic valuation when $K = \Qp$ 
and the usual valuation of a Laurent series when $K = k((t))$ --- and by 
$\Vert \cdot \Vert$ the corresponding norm.

@@

As a consequence of the above discussion, we derive the following 
proposition which can be directly combined with Proposition 3.12 of 
\cite{caruso-roe-vaccon:14a}.

\begin{prop}
\label{prop:boundLambdaf2}
Keeping the above notations, we have:
$$\Lambda(f)_{\leq 2} (x) \leq 2(x + \alpha + \mu) -
\min(\Lambda_h^{-1}(\nu) + \mu, \: \nu)$$
for all $x \leq \min(\Lambda_h^{-1}(\nu) - \alpha, \: \nu - \mu - \alpha)$. \todo{What is $\Lambda(f)_{\leq 2}$?}
\end{prop}

>>>>

\noindent
{\bf Notations.}
Throughout the paper, the letter $K$ will refer to a complete discrete 
valuation field of characteristic $0$. Usual examples are finite 
extensions of $\Qp$ and Laurent series fields over a field of 
characteristic $0$. We denote by $\val : K \to \Z \cup \{+\infty\}$ of 
$K$ --- it is the $p$-adic valuation when $K = \Qp$ and the usual 
valuation of a Laurent series when $K = k((t))$ --- and by $\Vert \cdot 
\Vert$ the corresponding norm.

@@

As a consequence of the above discussion, we derive the following 
proposition which can be directly combined with Proposition 3.12 of 
\cite{caruso-roe-vaccon:14a}. Following \cite{caruso-roe-vaccon:14a},
if $\varphi$ is a convex function and $v$ is a real number, we define
$$\varphi_{\geq v} : x \mapsto \inf_{y \geq 0} \big( \varphi(x+y)
- vy \big).$$
It is highest convex function with $\varphi_{\geq v} \leq \varphi$ and 
$\varphi'_{\geq v} \geq v$.

\begin{prop}
\label{prop:boundLambdaf2}
Keeping the above notations, we have:
$$\Lambda(f)_{\leq 2} (x) \leq 2(x + \alpha + \mu) -
\min(\Lambda_h^{-1}(\nu) + \mu, \: \nu)$$
for all $x \leq \min(\Lambda_h^{-1}(\nu) - \alpha, \: \nu - \mu - \alpha)$.
\end{prop}
